---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(out.width = "100%")
```


<!-- README.md is generated from README.Rmd. Please edit that file -->

# polyCheck <img src="https://avatars1.githubusercontent.com/u/43346405?s=200&v=4" align="right" height="50" width="50" />

[![Travis-CI Build Status](https://travis-ci.org/GRID3/polyCheck.svg?branch=master)](https://travis-ci.org/GRID3/polyCheck)

The package **polyCheck** provides functions which can be used to validate delineated polygons created as part of the GRID<sup>3</sup> project. The diagnostics check include:

- Polygon Geometry (area, perimeter, shape complexity etc.)
- Coordinate Reference Systems
- Polygon settlement type
- Does the polygon overlap previously surveyed areas.

It should be noted that the checks are designed to *support*, not *replace*, the manual verification process. It is still important that the outline of polygons is still 

## Installation

To install the package, you can use the function:

```
devtools::install_github("GRID3/polyCheck")
```

## User Guide

To see how to use the package check out the vignettes:

- [Basics](articles/Basics.html)
- [Interactive Maps](articles/InteractiveMaps.html)

## Quick Examples

The package provides some useful functions for plotting interactive maps displaying the polygon and survey points. A basic example is shown below, with more options explained within explained in the [Interactive Maps](articles/InteractiveMaps.html) section.

```{r, echo = FALSE}
library(polyCheck)
poly_path <- system.file("extdata/polygons/001_js_polygon.shp", package = "polyCheck")
display_polygon(poly_path)
```




