---
params:
  region: Kaduna
  polyPath: "../2_results"
  survey_points: "../1_data/survey_point/kaduna_strat_random_140.shp"
title: "`r paste0('Delineated Polygon Maps: ', params$region)`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
bibliography: "`r system.file('reportTemplates/software.bib', package = 'polyCheck')`"
---

```{css echo = FALSE}

pre {
  max-height: 300px;
  float: left;
  width: 910px;
  overflow-y: auto;
}

pre.r {
  max-height: none;
}

```


# About

This file provides summary maps of the delineated polygons. Depending on the number of maps displayed, the document may take a while to load all the basemaps. Basemaps are not available at a high zoom level for all regions, and therefore it may be required to zoom out for it to load.

# Map Results

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)


# Load Packages
library(polyCheck)
library(leaflet)
library(raster)

# Load Data
polyPath <- params$polyPath
polygons <- list_polygons(polyPath, sort = TRUE)
```

```{r, echo=FALSE,include = FALSE}
# This is a slight workaround to make the code loop work
maps <- display_polygon(polygons[1], params$survey_points)
htmltools::tagList(maps)
```

```{r, results='asis'}

for(i in polygons){
    cat("\n \n")
    cat(sprintf("##%s \n", basename(i)))
    map <- display_polygon(i, params$survey_points)
    print(htmltools::tagList(map))
    cat("\n \n")
    cat("\n \n")
}
```


-------

# About {-}

This document was produced using **rmarkdown** [@R-rmarkdown] with the maps being displayed using the **leaflet** [@R-leaflet] package. All custom scripts used for the polygon diagnostics are contained within the package **polyCheck** [@R-polyCheck].

The session info is provided below for reference:

```{r}
sessionInfo()
```


# References {-}
