---
params:
  filepath: ""
  root_dir: ""
  settlement_path: ""
  survey_points: ""
  ornl: ""
  reloadData: FALSE
title: "Validation of Delineated Polygons"
subtitle: "`r paste('Polygon ID:', basename(params$filepath))`"
date: "Last Updated: `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r knitrSetup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      out.width = "100%",
                      fig.align = "center")
```


```{r setup, include = FALSE, eval = params$reloadData}
# This chunk will only run if reloadData is set as TRUE. 
# This allows the document to quickly be run as a child document of a parent R Markdown document

# You may need to install bookdown if you haven't used it before
# install.packages("bookdown")
library(raster)
library(sp)
library(sf)
library(leaflet)
library(ggplot2)
library(rgeos)

# --- Load Data

# Settlement Seed
settlements <- params$settlement_path %>%
  shapefile()

# Survey Points
survey_points <- params$survey_points %>%
  shapefile()

survey_points$FID <- 0:(nrow(survey_points)-1) # Add FID to object

# load the ORNL data
ornl <- patams$ornl %>%
  shapefile()

```

# Shapefile Details

```{r loadShapefile}
shp_path <- params$filepath     # Select the shapefile
shp_name <- basename(shp_path)  # Extract the name
shp <- raster::shapefile(x = shp_path)  # Load the shapefile
shp
```

#  Location of Polygon

Figure \@ref(fig:polygonMap) shows the location of the polygon, relative to the survey point. **Note**, you may need to zoom out to view the basemaps as ESRI basemaps are not always available at a fully zoomed level.

```{r extractPointFromPoly}
id <- extract_id(shp_path)   # Extract the ID from the file name
survey_points_id <- survey_points[survey_points$FID == id,]
coords <- coordinates(survey_points_id)
```

```{r polygonMap, fig.cap = "Delineated Polygon"}
leaflet(shp, width = "100%") %>%
  addProviderTiles(provider = "Esri.WorldImagery") %>%
  addPolygons() %>%
  addMarkers(lng = coords[1], lat = coords[2])
```

```{r}
# Convert projection from degrees to metres
crs_m <- "+init=epsg:2062"
shp_m <- spTransform(shp, CRS(crs_m))
survey_points_id_m <- spTransform(survey_points_id, CRS(crs_m))

# Distance in kilometers
dist <- rgeos::gDistance(spgeom1 = shp_m, survey_points_id_m)/1000
```

```{r, results='asis', eval= dist!=0}
cat("**Note**: it appears that the polygon is not in the same location as the polygon. Make sure that the location is not an error")
```

```{r}
# Calculate hte intesection
points <- raster::intersect(settlements, shp)
num_points <- nrow(points)
```

We can verify the number of settlement points contained within the polygon. The region covers **`r nrow(points)`**. This value should be between 450 and 550.
